How Important are Usage Examples in REST API Documentation?

### 2017-03-08 controlled_study.tex
time graph addedxt

\begin{figure}

@@

@@

\caption{Quantitative Comparison between G1 and G2}
\label{fig:comparison}
\end{figure}

>>>>

\begin{figure*}

@@

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Time Spent (minutes),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=Time] {groupone_time.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=Time] {grouptwo_time.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

\end{tikzpicture}
\caption{Average Time Spent}
\label{graph:time}

@@

\caption{Quantitative Comparison between G1 and G2}
\label{fig:comparison}
\end{figure*}
